Berkeley Police Stop Data Maps

### 2016-08-08 eda/StopDataExploration/StopData_Maps.Rmd
still organizing

## Map 14
```{r}
bMap12 <- ggmap(berkMap) + 
geom_polygon(aes(x = long, y = lat, group = group), data = b3,
               colour = 'black', fill = 'white', alpha = .4, size = .3) +
  geom_point( data = mergedf, aes(x = long, y = lat), alpha = 0.2, size = 3, color = 'red' )
bMap12
```

>>>>

## Map 14
```{r}
bMap12 <- ggmap(berkMap) + 
geom_polygon(aes(x = long, y = lat, group = group), data = b3,
               colour = 'black', fill = 'white', alpha = .4, size = .3) +
  geom_point( data = mergedf, aes(x = long, y = lat), alpha = 0.2, size = 3, color = 'red' )
bMap12

ggmap(berkMap) +
  stat_density2d(aes(x = long, y = lat, fill= ..level.., alpha = .2* ..level..),
    size = 2, bins = 5, data = b3, geom = "polygon") +
  scale_fill_gradient(low = "black", high = "red") +
    theme (panel.grid.major = element_blank (), # remove major grid
		       panel.grid.minor = element_blank (),  # remove minor grid
		       axis.text = element_blank (), 
		       axis.title = element_blank (),
	         axis.ticks = element_blank ()) + 
  ggtitle("Population by census block group") +
  labs(alpha = element_blank())+
  guides(alpha = FALSE)
